---
title: "TINRO"
author: "Tim van der Stap"
date: "4/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
library(tidyverse)
library(lubridate)
library(readxl)
library(here)
library(worrms)
library(obistools)
library(parsedate)
library(googledrive)
library(uuid)
```

Download the data.

```{r file_download}
tinro_data_dictionary <- read_excel(here("IYS_data_template", "IYS2022_TINRO.xlsx"), sheet = "2. CRUISE_INSTRUMENT")
tinro_event_info <- read_excel(here("IYS_data_template", "IYS2022_TINRO.xlsx"), sheet = "4. SAMPLING EVENT INFO")
tinro_catch <- read_excel(here("IYS_data_template", "IYS2022_TINRO.xlsx"), sheet = "5. CATCH_FINAL INFO")
tinro_specimen <- read_excel(here("IYS_data_template", "IYS2022_TINRO.xlsx"), sheet = "6. SPECIMEN INFO")
```

Lets make the Event Core for the Trawl data collected. Please note that for the other Event Types (Bongo, Juday, CTD and Rosette) you can use the same 

```{r TINRO-event, eval = FALSE}
# For some reason, the Sampling_Duration_Minutes output is 0.04166667 - this has to be changed to accurately reflect minutes:
tinro_event_info$Sampling_Duration_Minutes <- difftime(tinro_event_info$Time_End, tinro_event_info$Time_Start, unit="mins") %>% as.numeric() %>% round()

tinro_event_info <- tinro_event_info %>% filter(Event_Type == "Trawl")
tinro_event_info$Time_Start <- strftime(tinro_event_info$Time_Start, "%H:%M:%S", tz = "UTC") # Use tz = "UTC" because otherwise the times are adjusted.
tinro_event_info$Time_End <- strftime(tinro_event_info$Time_End, "%H:%M:%S", tz = "UTC")

tinro_event_info$Year <- as.character(tinro_event_info$Year)
tinro_event_info$Month <- as.character(tinro_event_info$Month)
tinro_event_info$Day <- as.character(tinro_event_info$Day)
tinro_event_info <- tinro_event_info %>%
  mutate(eventDate_start = paste(Year, Month, Day, sep = "-")) %>%
  mutate(eventDate_start = format_iso_8601(as.POSIXct(paste(eventDate_start, Time_Start), tz = "UTC")),
         eventDate_start = str_replace(eventDate_start, "\\+00:00", "+12"),
         eventDate_finish = paste(Year, Month, Day, sep = "-")) %>%
  mutate(eventDate_finish = format_iso_8601(as.POSIXct(paste(eventDate_finish, Time_End), tz = "UTC")),
         eventDate_finish = str_replace(eventDate_finish, "\\+00:00", "+12"))
```

Confirm that the times and dates have been standardized correctly. In particular, confirm no sampling events spanned multiple days, and if so, fix accordingly:

``` {r trawl dates, eval = FALSE}
time_QAQC <- tinro_event_info %>% select(Station, Year, Month, Day, Time_Start, Time_End, eventDate_start, eventDate_finish) %>% print() 

# Change dates manually for Station 23
station23 <- tinro_event_info %>% filter(Station == 23) %>%
  mutate(eventDate_finish = as.Date(eventDate_finish) + 1) %>%
  mutate(eventDate_finish = paste0(eventDate_finish, "T", Time_End, "+12"))

tinro_event_info <- subset(tinro_event_info, Station != 23)
tinro_event_info <- rbind(tinro_event_info, station23) %>% arrange(Station)

# Create final eventDate and QC
tinro_event_info <- tinro_event_info %>%
  mutate(eventDate = paste(eventDate_start, eventDate_finish, sep = "/"))
obistools::check_eventdate(tinro_event_info)
```

Create Event Core.

``` {r event, eval = FALSE}
tinro_event_info_coordinates <- tinro_event_info %>%
  select(eventID = Station_Event_ID,
         Latitude_Start_DecDeg,
         Longitude_Start_DecDeg,
         Latitude_End_DecDeg,
         Longitude_End_DecDeg) %>%
  mutate(footprintWKT = paste("LINESTRING (", Longitude_Start_DecDeg, Latitude_Start_DecDeg, ",", 
                              Longitude_End_DecDeg, Latitude_Start_DecDeg, ")")) 
tinro_event_info_linestring <- obistools::calculate_centroid(tinro_event_info_coordinates$footprintWKT)
tinro_event_info_linestring <- cbind(tinro_event_info_coordinates, tinro_event_info_linestring) %>%
  select(eventID, footprintWKT, decimalLatitude, decimalLongitude, coordinateUncertaintyInMeters)

tinro2022_event <- tinro_event_info %>%
  select(eventID = Station_Event_ID,
         eventDate, Year, Month, Day,
         minimumDepthInMeters = Minimum_Sampling_Depth_Meters,
         maximumDepthInMeters = Maximum_Sampling_Depth_Meters,
         sampleSizeValue = Sampling_Duration_Minutes) %>%
  left_join(tinro_event_info_linestring, by = "eventID") %>%
  mutate(geodeticDatum = "WGS84",
         institutionCode = "TINRO",
         institutionID = "https://edmo.seadatanet.org/report/917",
         samplingEffort = "midwater trawl",
         sampleSizeUnit = "minutes") %>%
  distinct(eventID, .keep_all = TRUE)

write_csv(tinro2022_event, here("standardized_data", "tinro2022_event.csv"))
```

Always good to add in some QAQC to ensure the Event Core does not contain any duplicate eventIDs, weird dates or observations on land.

```{r eventCore QAQC, eval = FALSE}
report <- obistools::report(tinro2022_event) %>% print()
eventid <- obistools::check_eventids(tinro2022_event)
depth <- obistools::check_depth(tinro2022_event) %>% print()
```

Next, create the occurrence extension for the overall taxa observed in the catches. 

```{r occurrence, eval = FALSE}
tinro_occ <- tinro_catch %>%
  select(eventID = Station_Event_ID,
         occurrenceID = Catch_ID,
         scientificName = Scientific_Name,
         taxonRank = Taxonomic_rank,
         Lifestage,
         vernacularName = common_name,
         identifiedBy,
         dateIdentified,
         individualCount = Catch_count) 

tinro_occ$identificationQualifier <- ifelse(grepl("\\b sp.",  tinro_occ$scientificName), "sp. inc.", NA)
tinro_occ$scientificName <- gsub(" sp.", "", tinro_occ$scientificName)

worms <- worrms::wm_records_names(unique(tinro_occ$scientificName)) %>% bind_rows() # Two species names are written wrong
tinro_occ$scientificName <- gsub("Phacellophora camtshchatica", "Phacellophora camtschatica", tinro_occ$scientificName)
tinro_occ$scientificName <- gsub("Oncorhynchus tschawytscha", "Oncorhynchus tshawytscha", tinro_occ$scientificName)
worms <- worrms::wm_records_names(unique(tinro_occ$scientificName)) %>% bind_rows() %>%
  select(scientificName = scientificname,
         scientificNameAuthorship = authority,
         kingdom, phylum, class, order, family, genus,
         scientificNameID = lsid)

tinro_occ_fnl <- left_join(tinro_occ, worms, by = "scientificName") %>%
  mutate(specificEpithet = stringr::word(scientificName, 2),
         occurrenceStatus = "present")
```

Next, create an occurrence extension for the individual specimen that were identified and measured. This occurrence extension will then have to be combined with the overall catch occurrence extension:

```{r specimen, eval=FALSE}
tinro_specimen_occ <- tinro_specimen %>%
  select(eventID = Station_Event_ID,
         occurrenceID = Specimen_ID,
         scientificName = Scientific_Name,
         taxonRank = Taxonomic_rank,
         vernacularName = common_name,
         sex = Sex,
         lifeStage = Lifestage)

tinro_specimen_occ$identificationQualifier <- ifelse(grepl("\\b sp.",  tinro_specimen_occ$scientificName), "sp. inc.", NA)
tinro_specimen_occ$scientificName <- gsub(" sp.", "", tinro_specimen_occ$scientificName)

tinro_specimen_occ$scientificName <- gsub("Phacellophora camtshchatica", "Phacellophora camtschatica", tinro_specimen_occ$scientificName)
tinro_specimen_occ$scientificName <- gsub("Oncorhynchus tschawytscha", "Oncorhynchus tshawytscha", tinro_specimen_occ$scientificName)

worms_specimen <- worrms::wm_records_names(unique(tinro_specimen_occ$scientificName)) %>% bind_rows() %>%
  select(scientificName = scientificname,
         scientificNameAuthorship = authority,
         kingdom, phylum, class, order, family, genus,
         scientificNameID = lsid)

tinro_specimen_fnl <- left_join(tinro_specimen_occ, worms_specimen, by = "scientificName")
tinro_specimen_fnl <- tinro_specimen_fnl %>%
  mutate(specificEpithet = stringr::word(scientificName, 2),
         occurrenceStatus = "present")
```

Combine both occurrence extensions into a single data table: 

```{r final tinro catch, eval = FALSE}
tinro2022_trawl_occ <- dplyr::bind_rows(tinro_occ_fnl, tinro_specimen_fnl) %>%
  mutate(basisOfRecord = "HumanObservation")

# To re-order the occurrenceID, use following code:
order <- stringr::str_sort(tinro2022_trawl_occ$occurrenceID, numeric=TRUE)
tinro2022_trawl_occ <- tinro2022_trawl_occ[match(order, tinro2022_trawl_occ$occurrenceID),]

# Remove the NAs from the individualCount column:
tinro2022_trawl_occ$individualCount[is.na(tinro2022_trawl_occ$individualCount)] <- ""

write_csv(tinro2022_trawl_occ, here("standardized_data", "tinro2022_trawl_occ.csv"))
```

Create a resourceRelationship extension data table to indicate that specimen data are part of the overall catch data:

```{r resourceRelationship, eval = FALSE}
tinro_resourceRelationship <- tinro2022_trawl_occ %>%
  select(eventID, occurrenceID, scientificName, individualCount) %>%
  mutate(resourceID = ifelse(tinro2022_trawl_occ$individualCount == "", tinro2022_trawl_occ$occurrenceID, NA)) %>%
  group_by(eventID, scientificName) %>%
  filter(n() != 1) %>%
  ungroup()

tinro_resourceRelationship <- tinro_resourceRelationship %>%
  mutate(relatedResourceID = ifelse(is.na(tinro_resourceRelationship$resourceID), tinro_resourceRelationship$occurrenceID, NA)) %>%
  mutate(relationshipOfResource = ifelse(!is.na(resourceID), "is a subset of", NA)) %>%
  dplyr::arrange(eventID, scientificName) %>%
  fill(relatedResourceID) %>%
  filter(!is.na(resourceID))

order <- stringr::str_sort(tinro_resourceRelationship$resourceID, numeric = TRUE)

tinro_resourceRelationship <- tinro_resourceRelationship[match(order, tinro_resourceRelationship$resourceID),]
tinro_resourceRelationship <- tinro_resourceRelationship %>%
  mutate(resourceRelationshipID = paste(relatedResourceID, "rr", sep = "-"),
         ID = sprintf("%03d", row_number()),
         resourceRelationshipID = paste(resourceRelationshipID, ID, sep = "-")) %>%
  select(eventID, resourceRelationshipID, resourceID, relationshipOfResource, relatedResourceID)

write_csv(tinro_resourceRelationship, here("standardized_data", "tinro2022_resourceRelationship.csv"))
```

Create an extended measurementOrFact (eMOF) extension, by creating multiple data tables and combining them:

```{r TINRO RV, eval = FALSE}
tinro_trawl2022_rv <- tinro_event_info %>% filter(Event_Type == "Trawl") %>%
  select(eventID = Station_Event_ID,
         measurementValue = Vessel_Name_Abbr) %>%
  mutate(measurementType = "Research Vessel",
         measurementTypeID = "http://vocab.nerc.ac.uk/collection/L06/current/31/",
         measurementValueID = "http://vocab.nerc.ac.uk/collection/C17/current/90TN/", #deprecated so have to find replacement..?
         measurementUnit = NA,
         measurementUnitID = NA,
         measurementID = paste(eventID, measurementType, sep = "-")) %>% distinct()
```

Next, information on bottomdepth during the trawl is added:

```{r TINRO bottomdepth, eval = FALSE}
tinro_trawl2022_bottomdepth <- tinro_event_info %>% filter(Event_Type == "Trawl") %>%
  select(eventID = Station_Event_ID,
         Bottom_Depth_Meters) %>%
  mutate_all(as.character) %>%
  pivot_longer(cols = Bottom_Depth_Meters,
               names_to = "measurementType",
               values_to = "measurementValue") %>%
  mutate(measurementTypeID = case_when(
    measurementType == "Bottom_Depth_Meters" ~ "http://vocab.nerc.ac.uk/collection/P09/current/BATH/"),
    measurementUnit = "meters",
    measurementUnitID = case_when(
      measurementUnit == "meters" ~ "http://vocab.nerc.ac.uk/collection/P06/current/ULAA/"),
      measurementValueID = NA,
    measurementID = paste(eventID, measurementType, sep = "-")) %>%
  select(eventID, measurementID, measurementType, measurementTypeID, measurementValue, measurementValueID,
         measurementUnit, measurementUnitID)
```

Sampling instrument parameters:

```{r sampling instrument, eval = FALSE}
tinro_sampling_stations <- tinro_event_info %>% filter(Event_Type == "Trawl") %>% select(Station_Event_ID)

tinro_samplingInstrument <-  tinro_data_dictionary %>% filter(`Cruise / Instrument` == "Trawl") %>%
  filter(Attribute %in% c("Gear_type", "Mesh_Size", "Cod-end_Mesh_Size", "Net_Length", "Net_Width", "Net_Height")) %>%
  select(measurementType = Attribute, 
         measurementValue = Value)

tinro_samplingInstrument <- merge(tinro_sampling_stations, tinro_samplingInstrument) %>%
  rename(eventID = Station_Event_ID) %>%
  mutate_all(as.character) %>%
  mutate(measurementTypeID = case_when(
    measurementType == "Gear_type" ~ "http://vocab.nerc.ac.uk/collection/Q01/current/Q0100002/",
    measurementType == "Mesh_Size" ~ "http://vocab.nerc.ac.uk/collection/Q01/current/Q0100015/",
    measurementType == "Cod-end_Mesh_Size" ~ "http://vocab.nerc.ac.uk/collection/Q01/current/Q0100015/", 
    measurementType == "Net_Length" ~ " ",
    measurementType == "Net_Width" ~ "http://vocab.nerc.ac.uk/collection/Q01/current/Q0100014/",
    measurementType == "Net_Height" ~ "http://vocab.nerc.ac.uk/collection/Q01/current/Q0100013/"),
    measurementUnit = case_when(
      measurementType %in% c("Mesh_Size", "Cod-end_Mesh_Size") ~ "millimeters",
      measurementType %in% c("Net_Length", "Net_Width", "Net_Height") ~ "meters"),
    measurementUnitID = case_when(
      measurementUnit == "millimeters" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UXMM/",
      measurementUnit == "meters" ~ "http://vocab.nerc.ac.uk/collection/P06/current/ULAA/"),
    measurementValueID = case_when(
      measurementType == "Gear_type" ~ " "),
    measurementID = paste(eventID, measurementType, sep = "-")) %>%
  select(eventID, measurementID, measurementType, measurementTypeID, measurementValue, measurementValueID,
         measurementUnit, measurementUnitID)
```

Measurements pertaining to the sampling effort: 

```{r samplingEffort, eval = FALSE}
tinro_trawl2022_samplingEffort <- tinro_event_info %>% filter(Event_Type == "Trawl") %>%
  select(eventID = Station_Event_ID,
         Sampling_Duration_Minutes,
         Tow_speed_kilometers_per_hour,
         Tow_distance_nautical_miles)

tinro_trawl2022_samplingEffort <- tinro_trawl2022_samplingEffort %>%
  mutate_all(as.character) %>%
  pivot_longer(cols = Sampling_Duration_Minutes:Tow_distance_nautical_miles,
               names_to = "measurementType",
               values_to = "measurementValue") %>%
  mutate(measurementTypeID = case_when(
    measurementType == "Tow_distance_nautical_miles" ~ "http://vocab.nerc.ac.uk/collection/P01/current/LENTRACK/",
    measurementType == "Tow_speed_kilometers_per_hour" ~ "http://vocab.nerc.ac.uk/collection/P01/current/TOWSPEED/",
    measurementType == "Sampling_Duration_Minutes" ~ "http://vocab.nerc.ac.uk/collection/P01/current/AZDRZZ01/"),
    measurementUnit = case_when(
      measurementType == "Tow_distance_nautical_miles" ~ "nautical miles",
      measurementType == "Tow_speed_kilometers_per_hour" ~ "kilometers per hour",
      measurementType == "Sampling_Duration_Minutes" ~ "minutes"),
    measurementUnitID = case_when(
      measurementUnit == "minutes" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UMIN/",
      measurementUnit == "kilometers per hour" ~ "http://vocab.nerc.ac.uk/collection/P06/current/KMHR/",
      measurementUnit == "nautical miles" ~ "http://vocab.nerc.ac.uk/collection/P06/current/NTML/"),
    measurementValueID = NA,
    measurementID = paste(eventID, measurementType, sep = "-")) %>%
  select(eventID, measurementID, measurementType, measurementTypeID, measurementValue, measurementValueID,
         measurementUnit, measurementUnitID)
```

And for the environmental variables:

```{r environmental variables, eval = FALSE}
tinro2022_env <- tinro_event_info %>% filter(Event_Type == "Trawl") %>%
  select(eventID = Station_Event_ID,
         Wind_Direction_Degrees,
         Wind_Speed_kilometers_per_hour,
         Wave_height_Meters,
         Swell_height_Meters) %>%
  mutate_all(as.character) %>%
  pivot_longer(cols = Wind_Direction_Degrees:Swell_height_Meters,
               names_to = "measurementType",
               values_to = "measurementValue") %>%
  mutate(measurementTypeID = case_when(
    measurementType == "Wind_Direction_Degrees" ~ "http://vocab.nerc.ac.uk/collection/B39/current/relwinddir/",
    measurementType == "Wind_Speed_kilometers_per_hour" ~ "http://vocab.nerc.ac.uk/collection/P07/current/CFSN0038/",
    measurementType == "Wave_height_Meters" ~ "http://vocab.nerc.ac.uk/collection/P07/current/JNQS0CMX/",
    measurementType == "Swell_height_Meters" ~ "http://vocab.nerc.ac.uk/collection/P09/current/SWHT/"),
    measurementUnit = case_when(
      measurementType == "Wind_Direction_Degrees" ~ "degrees",
      measurementType == "Wind_Speed_kilometers_per_hour" ~ "kilometers per hour",
      measurementType == "Wave_height_Meters" ~ "meters",
      measurementType == "Swell_height_Meters" ~ "meters"),
    measurementUnitID = case_when(
      measurementUnit == "meters" ~ "http://vocab.nerc.ac.uk/collection/P06/current/ULAA/",
      measurementUnit == "degrees" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UAAA/",
      measurementUnit == "kilometers per hour" ~ "http://vocab.nerc.ac.uk/collection/P06/current/KMHR/"),
    measurementValueID = NA,
    measurementID = paste(eventID, measurementType, sep = "-")) %>%
  drop_na(measurementValue) %>%
  select(eventID, measurementID, measurementType, measurementTypeID, measurementValue, measurementValueID,
         measurementUnit, measurementUnitID)
```

Next two eMOF extensions are created with measurements pertaining to overall species' catch weight at each trawl, and individual length and weight measurements. For some of these parameters a value is not recorded (ie. they show up as _NA_), and these records are dropped from the final emof extension. The lifeStage is populated in the Occurrence extension section.

```{r TINRO All-catch eMoF, eval = FALSE}
tinro2022_trawl_allcatch_emof <- tinro_catch %>%
  select(eventID = Station_Event_ID, 
         occurrenceID = Catch_ID,
         individualCount = Catch_count,
         Catch_weight,
         lifeStage = Lifestage) %>%
  mutate_all(as.character) %>%
  pivot_longer(cols = individualCount:lifeStage,
               names_to = "measurementType",
               values_to = "measurementValue") %>%
  mutate(measurementID = paste(occurrenceID, measurementType, sep = "-"),
         measurementTypeID = case_when(
           measurementType == "Catch_weight" ~ "http://vocab.nerc.ac.uk/collection/S06/current/S0600088/",
           measurementType == "individualCount" ~ "http://vocab.nerc.ac.uk/collection/P01/current/OCOUNT01/",
           measurementType == "lifeStage" ~ "http://vocab.nerc.ac.uk/collection/P01/current/LSTAGE01/"),
         measurementUnit = case_when(
           measurementType == "Catch_weight" ~ "kilogram",
           measurementType == "individualCount" ~ "individuals"),
         measurementUnitID = case_when(
           measurementUnit == "kilogram" ~ "http://vocab.nerc.ac.uk/collection/P06/current/KGXX/",
           measurementUnit == "individuals" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UUUU/"),
         measurementValueID = case_when(
           measurementValue == "Juvenile" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1127/",
           measurementValue == "adult" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1116/",
           measurementValue == "immature" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1171/")) %>%
  select(eventID, occurrenceID, measurementID, measurementType, measurementTypeID, measurementValue, measurementValueID,
         measurementUnit, measurementUnitID)
```

Next, create the emof for specimen data:

```{r TINRO Specimen emof, eval = FALSE}
tinro2022_specimen_emof <- tinro_specimen %>%
  select(eventID = Station_Event_ID, 
         occurrenceID = Specimen_ID,
         Sex,
         lifeStage = Lifestage,
         Specimen_Length,
         Specimen_Length2,
         Specimen_Weight,
         Specimen_Weight_without_organs = Specimen_Weight2,
         individualCount = Number_measured,
         Length_Type, Length_Type2) %>%
  mutate_all(as.character) %>%
  pivot_longer(cols = Sex:individualCount,
               names_to = "measurementType",
               values_to = "measurementValue") %>%
  mutate(measurementID = paste(occurrenceID, measurementType, sep = "-"),
         measurementType = ifelse(measurementType == "Specimen_Length" & Length_Type == "Fork length", "Specimen fork length", measurementType),
         measurementType = ifelse(measurementType == "Specimen_Length" & Length_Type == "Total length", "Specimen total length", measurementType),
         measurementType = ifelse(measurementType == "Specimen_Length" & Length_Type == "Mantle length", "Specimen mantle length", measurementType),
         measurementType = ifelse(measurementType == "Specimen_Length" & Length_Type == "Bell diameter", "Specimen bell diameter", measurementType),
         measurementType = ifelse(measurementType == "Specimen_Length2" & Length_Type2 == "Standard length", "Specimen standard length", measurementType),
         measurementTypeID = case_when(
           measurementType == "Sex" ~ "http://vocab.nerc.ac.uk/collection/P01/current/ENTSEX01/",
           measurementType == "lifeStage" ~ "http://vocab.nerc.ac.uk/collection/P01/current/LSTAGE01/",
           measurementType == "Specimen total length" ~ "http://vocab.nerc.ac.uk/collection/P01/current/TL01XX01",
           measurementType == "Specimen fork length" ~ "http://vocab.nerc.ac.uk/collection/P01/current/FL01XX01/",
           measurementType == "Specimen mantle length" ~ "http://vocab.nerc.ac.uk/collection/P01/current/DML1XX01/",
           measurementType == "Specimen bell diameter" ~ "http://vocab.nerc.ac.uk/collection/P01/current/OBSINDDM/",
           measurementType == "Specimen standard length" ~ "http://vocab.nerc.ac.uk/collection/P01/current/SL01XX01/",
           measurementType == "individualCount" ~ "http://vocab.nerc.ac.uk/collection/P01/current/OCOUNT01/",
           measurementType == "Specimen_Weight" ~ "http://vocab.nerc.ac.uk/collection/S06/current/S0600088/",
           measurementType == "Specimen_Weight_without_organs" ~ " "),
         measurementUnit = case_when(
           measurementType %in% c("Specimen fork length", "Specimen total length", "Specimen mantle length",
                                  "Specimen bell diameter", "Specimen standard length") ~ "millimeters",
           measurementType %in% c("Specimen_Weight", "Specimen_Weight_without_organs") ~ "grams",
           measurementType == "individualCount" ~ "individuals"),
         measurementUnitID = case_when(
           measurementUnit == "millimeters" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UXMM/",
           measurementUnit == "grams" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UGRM/",
           measurementUnit == "individuals" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UUUU/"),
         measurementValueID = case_when(
           measurementValue == "adult" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1116/",
           measurementValue == "Juvenile" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1127/",
           measurementValue == "immature" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1171/",
           measurementValue == "Female" ~ "http://vocab.nerc.ac.uk/collection/S10/current/S102/",
           measurementValue == "Male" ~ "https://vocab.nerc.ac.uk/collection/S10/current/S103/",
           measurementValue == "N" ~ "https://vocab.nerc.ac.uk/collection/S10/current/S105/")) %>%
  select(eventID, occurrenceID, measurementID, measurementType, measurementTypeID, measurementValue, measurementValueID,
         measurementUnit, measurementUnitID)
```

Combine the emof data tables and save:

```{r TINRO Trawl emof, eval = FALSE}
tinro2022_trawl_eMOF_sampling <- dplyr::bind_rows(
                                   tinro_trawl2022_rv,
                                   tinro_trawl2022_bottomdepth,
                                   tinro_samplingInstrument,
                                   tinro_trawl2022_samplingEffort,
                                   tinro2022_env)

tinro2022_trawl_eMOF_catch <- dplyr::bind_rows(tinro2022_trawl_allcatch_emof, 
                                   tinro2022_specimen_emof)

tinro2022_eMOF <- dplyr::bind_rows(tinro2022_trawl_eMOF_sampling, tinro2022_trawl_eMOF_catch)

# Drop any measurementValue fields with NAs - these are not informative. 
tinro2022_eMOF <- tinro2022_eMOF %>% filter(!is.na(measurementValue))

write_csv(tinro2022_eMOF, here("standardized_data", "tinro2022_eMOF.csv"))
```